Proposal Thesis

### 2023-06-01 Thesis/Proposal Thesis/Present/Proposal Thesis.Rmd
Draft

@@

df_1 = df_1 %>% rename(bahan_baku = code_gula,
                       harga      = harga_gula) %>% 
       select(-multiplicator,-cost_obj_func)

colnames(df_2)[2:7] = paste0("bahan_baku_",1:6)

```

>>>>

format_money = function(x) {
  paste0("Rp", formatC(as.numeric(x), format="f", digits=0, big.mark=","))
}

df_1 = df_1 %>% rename(bahan_baku = code_gula,
                       harga      = harga_gula) %>% 
       select(-multiplicator,-cost_obj_func) %>% 
       mutate(harga = format_money(harga))

colnames(df_2)[2:7] = paste0("bahan_baku_",1:6)
df_2[is.na(df_2)] = 0
```

@@

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(kableExtra)
df_1 %>% 
  knitr::kable(caption = "Spek Bahan Baku") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  add_header_above(c(" " = 1,"Informasi Detail" = 5))
```

## Komposisi Bahan Baku per Produk

```{r,echo=FALSE,message=FALSE,warning=FALSE}
df_2 %>% 
  head(10) %>%
  knitr::kable(caption = "Produk apa bisa dibuat menggunakan bahan baku yang mana?\nSampel 10 produk") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  add_header_above(c(" " = 1,"Bahan Baku" = 6))
```
